Preserving Reciprocal Consistency in Distributed Graph Databases

### 2020-04-06 paper/dist-graphdb.tex
some paul changes

A distributed graph database employs a shared-nothing architecture, partitioning a graph between a number of loosely cooperating servers. Graph partitioning is non-trivial and a common approach is to use a $k$-balanced edge cut \cite{Huang2016}. The objective of such an approach is to minimize the proportion of edges that span partitions in a manner that balances the distribution of vertices to partitions. Intra-partition edges are referred to as \textit{local edges} and inter-partition edges are referred to as \textit{distributed edges}, Figure \ref{dist-graph}. The proportion of distributed edges is always non-negligible ranging from 25-75\% \cite{Huang2016}.

>>>>

A distributed graph database employs a shared-nothing architecture, partitioning a graph between a number of loosely cooperating servers.
Graph partitioning is non-trivial and a common approach is to use a $k$-balanced edge cut \cite{Huang2016}.
The objective of such an approach is to minimize the proportion of edges that span partitions in a manner that balances the distribution of vertices to partitions.
Figure \ref{dist-graph} depicts a graph database partitioned across 3 servers, $S1$, $S2$ and $S3$.
Intra-partition edges are referred to as \textit{local edges} and inter-partition edges are referred to as \textit{distributed edges} (shown with dashed lines in Figure \ref{dist-graph}).
The proportion of distributed edges is always non-negligible ranging from 25-75\% \cite{Huang2016}.

### 2020-04-06 paper/reciprocal-consistency.tex
some paul changes

In the property graph data model edges have direction, each edge having a pair of \emph{source} and \emph{destination} vertices. In the storage layer, edge information is stored with \textbf{both} the source and destination vertices. This allows an edge to be traversed in both directions at the same cost, facilitating improved query performance.

A common approach to storing graphs (arising from JanusGraph \cite{janusgraph} and TitanDB \cite{TitanDB}) is for database records to represent vertices containing both properties and an adjacency list containing edge \emph{pointers} to other vertices, Figure \ref{adj-list}. Consider, for example, the statement that Tolkien \textit{wrote} The Hobbit. It is expressed using vertices \emph{a} and \emph{b}, for Tolkien and The Hobbit respectively, and an edge \textit{wrote} running from \emph{a} (source) to \emph{b} (destination).

@@

Adjacency lists of both \emph{a} and \emph{b} record information about the edge and this information is mutually reciprocal (or inverse) of each other: \emph{a}'s list will indicate `\emph{a} \emph{wrote} \emph{b}' while \emph{b}'s will have `\emph{b} \emph{written} by \emph{a}', Figure \ref{reciprocally-consistent-edge}. Thus, a query `list all titles by the author who wrote The Hobbit' can be answered starting at (destination vertex) \emph{b} and then traversing to (source vertex) \emph{a}, even though the edge is ``directed'' from \emph{a} to \emph{b} at model level abstraction. When the adjacency list entries for a given edge are mutually compatible like this, that edge is said to be \emph{reciprocally consistent}, a form of referential integrity. A query can read either the source or destination vertex and is able to reify the edge correctly, returning consistent results.

>>>>

In the property graph data model edges have direction, each edge having a pair of \emph{source} and \emph{destination} vertices.
In the storage layer, edge information is stored with \textbf{both} the source and destination vertices.
This, as we explain next, allows an edge to be traversed in both directions and thus facilitates improved query performance.

A common approach to storing graphs (arising from JanusGraph \cite{janusgraph} and TitanDB \cite{TitanDB}) is given in Figure \ref{adj-list}.
A vertex is represented by a record that contains one or more vertex properties and a sequence of edge pointers (each shown simply as edge in Figure \ref{adj-list}) pointing to other vertices.
This sequence of edge pointers is referred to as an adjacency list.

Consider, for example, the statement that Tolkien \textit{wrote} The Hobbit.
It is expressed using vertices \emph{a} and \emph{b}, for Tolkien and The Hobbit respectively, and an edge \textit{wrote} running from \emph{a} (source) to \emph{b} (destination).

@@

Adjacency lists of both \emph{a} and \emph{b} record information about the edge and this information is reciprocal (or inverse) of each other: \emph{a}'s list will indicate `\emph{a} \emph{wrote} \emph{b}' while \emph{b}'s will have `\emph{b} \emph{written} by \emph{a}', Figure \ref{reciprocally-consistent-edge}. Thus, a query `list all titles by the author who wrote The Hobbit' can be answered starting at (destination vertex) \emph{b} and then traversing to (source vertex) \emph{a}, even though the edge is ``directed'' from \emph{a} to \emph{b} at model level abstraction. When the adjacency list entries for a given edge are mutually compatible like this, that edge is said to be \emph{reciprocally consistent}, a form of referential integrity. A query can read either the source or destination vertex and is able to reify the edge correctly, returning consistent results.
